CPP_analysis

### 2019-10-02 CPP_analysis.Rmd
Calculate dates

```{r message=FALSE, include=FALSE}
install.packages("knitr")
install.packages("tidyverse") #1.2.1
install.packages("drc") #3.0.1
install.packages("stringr")
```

```{r message=FALSE}
library("drc") #3.0.1
library("knitr")
library("tidyverse") #1.2.1
library("stringr")
```

@@

>>>>

```{r message=FALSE, include=FALSE}
install.packages("knitr")
install.packages("tidyverse") #1.2.1
install.packages("drc") #3.0.1
install.packages("stringr")
install.packages("geosphere")
install.packages("lubridate")
```

```{r message=FALSE}
library("drc") #3.0.1
library("knitr") #1.25
library("tidyverse") #1.2.1
library("stringr") #1.4.0
library("geosphere") #1.5.10
library("lubridate") #1.7.4
```

@@

```{r day_function}
findDate<-function(lat, pp, year) {
#generate day lengths at latitude between July 1 and Dec 31
x<-daylength(lat,182:365)
#find closest day length in vector
daynumber<-which.min(abs(x-pp))
#convert day number to date
origin<-as.character(paste(year, "-07-01",sep=""))
return(as.character(as.Date(daynumber, origin=origin)))
}

```{r}
cpp_2$date<-mapply(findDate, lat=cpp_2$lat, pp=cpp_2$Estimate, year=cpp_2$year)
cpp_2$date_again<-format(as.Date(cpp_2$date), "%mm-%dd")
cpp_2$date_again<-as.Date(cpp_2$date_again, format="%mm-%dd")
ggplot(filter(cpp_2, year!=1988), aes(x=lat, y=date_again, color=year)) + geom_point() + scale_y_date(date_breaks = "weeks" , date_minor_breaks="days", date_labels = "%b-%d") + facet_grid(~country) + theme_bw()
```
